Outline of Ideas for BTC Transaction Frequency

### 2015-10-08 outline/outline.tex
tweaked the seasonal effects model

The full model can then be written as
\begin{align*}
t_k|t_{1:(k-1)}, \tau_{1:K} &\sim LN(\log(\tau_k) - \sigma^2/2, \sigma)\mathbbm{1}(t_k > m_k)\\
x_{\tau_{k+1}} - x_{\tau_{k}}|\tau_{1:K} & \stackrel{ind}{\sim} G\left(\beta(\gamma_{\tau_k + \delta_k} - \gamma_{\tau_k}),\beta\right)\\
\gamma_{\tau_k + \delta_k}|\gamma_{\tau_k} & \sim LN(\left(e^{-\phi\delta}(\log\gamma_{\tau_k} - \mu_{\tau_k}) + \mu_{\tau_k + \delta_k}, \frac{\sigma_{\varepsilon}^2}{2\phi}\left[1 - e^{-2\phi\delta}\right]\right)\\
\delta_{k} = \tau_{k+1} - \tau_{k} &\stackrel{iid}{\sim} Exp(1/10)
\end{align*}
for blocks $k=1,2,\dots,N$ where $\mu_{\tau}$ is a parameterized deterministic function of $\tau$. For example, a trend with seasonal variability can be obtained via $\mu_{\tau} = \alpha_0 + \alpha_1\tau + \alpha_2\sin(\omega \tau)$ where $alpha_{0:2}$ is an uknown parameter and $\omega$ is the known frequency of the seasonal effect.

>>>>

The full model can then be written as
\begin{align*}
t_k|t_{1:(k-1)}, \tau_{1:K} &\sim LN(\log(\tau_k) - \sigma^2/2, \sigma)\mathbbm{1}(t_k > m_k)\\
x_{\tau_{k+1}} - x_{\tau_{k}}|\tau_{1:K} & \stackrel{ind}{\sim} G\left(\beta(\gamma_{\tau_k + \delta_k} - \gamma_{\tau_k}),\beta\right)\\
\gamma_{\tau_k + \delta_k}|\gamma_{\tau_k} & \sim LN(\left(e^{-\phi\delta}(\log\gamma_{\tau_k} - \mu_{\tau_k}) + \mu_{\tau_k + \delta_k}, \frac{\sigma_{\varepsilon}^2}{2\phi}\left[1 - e^{-2\phi\delta}\right]\right)\\
\delta_{k} = \tau_{k+1} - \tau_{k} &\stackrel{iid}{\sim} Exp(1/10)
\end{align*}
for blocks $k=1,2,\dots,N$ where $\mu_{\tau}$ is a parameterized deterministic function of $\tau$. For example, a trend with seasonal variability can be obtained via $\mu_{\tau} = \alpha_0 + \alpha_1\tau + \alpha_2\sin(2\pi f \tau + \lambda)$ where $alpha_{0}$, $\alpha_1$, $\alpha_2$, and $\lambda$ are uknown parameters and $f$ is the known frequency of the seasonal effect.
